The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-17 paper/Analisis.tex
New plot showing the Off center set up

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ and 
we moved $0.2 R$ in the x axis.

>>>>

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ and 
we moved $0.2 R$ in the x axis.

\begin{figure}
\includegraphics[scale=0.3]{OF_spheres.png}
\caption{The two solid circles show up the photons we select in order to make the anisotropic emission
		rotation is defined to be $\mathrm{z}$-axis. we also select photons in the negative side of 				        $\mathrm{x}$ (dashed circles) in order to see the complete effect of rotation. 
   \label{fig:OCspheres}} 
\end{figure}
